Fast Fashion's Rapid Rate of Overproduction is Observedly Unsustainable & Unethical: Why and How did we get here?

### 2023-04-21 outputs/paper.qmd
Paper edits

This paper delves into a case study of the fast fashion company ZAFUL. The population I hope to generalize the results to in this case is all fashion/apparel-focused companies that would be considered to be participating in fast-fashion. The estimand that I aim to approach is these companies' rate of producing new products and retiring old products. By documenting all available products in one of ZAFUL's given categories through web scraping and comparing the data collected on different dates over time, we see first-hand the unbelievably fast rate of production and turnover. The extremity of these results are further emphasized when compared to the product retention rate of a sustainable fashion company, KOTN.

@@

The gathering of the data used for this paper was done by web scraping through the statistical programming language R @citeR and the Chrome extension Web Scraper @citeWS which were conducted on the sites zaful.com and kotn.com. Further... (package citations).

@@

```{r}
#| echo: false
#| include: false
# talk about data collection process and category (women's clothing only)
# web scraper chrome extension for kotn (dynamic webpage)
# looping through pagination for zaful 
# head of both stores
# summarize total number of products seen before and after for two stores 
```

@@

```{r}
#| echo: false
#| include: false
# semi_join(before, after) to see what is the same
# use anti_join(before, after) to see what has been removed
# anti_join(after, before) to see what has been added
# make a table with those 3 values 
# make pi-chart with values proportionate to total number of products
# make point/line graph showing increase of new products and decrease of old products
# bar graph showing how much changed in store 1 vs store 2

#z_products <- read_csv(here::here("inputs/data/zafulapril2.csv"), show_col_types = FALSE)

#z_products2 <- read_csv(here::here("inputs/data/zafulapril4.csv"), show_col_types = FALSE)

#k_products <- read_csv(here::here("inputs/data/kotnapril2.csv"), show_col_types = FALSE)

#k_products2 <- read_csv(here::here("inputs/data/kotnapril4.csv"), show_col_types = FALSE)

#samek <- semi_join(k_products, k_products2)
#removedk <- anti_join(k_products, k_products2)
#addedk <- anti_join(k_products2, k_products)

#samez <- semi_join(z_products, z_products2)
#removedz <- anti_join(z_products, z_products2)
#addedz <- anti_join(z_products2, z_products)

>>>>

This paper delves into a case study of the fast fashion company ZAFUL. By documenting all available products in one of ZAFUL's given categories through web scraping and comparing the data collected on different dates over time, we see first-hand the unbelievably fast rate of production and turnover. The extremity of these results are further emphasized when compared to the product retention rate of a sustainable fashion company, KOTN.

@@

The gathering of the data used for this paper was done by web scraping through the statistical programming language `R` [@citeR], the packages `rvest` [@citeVest], `httr` [@citeHTTR], and the Chrome extension *Web Scraper* [@citeWS] which were conducted on the sites zaful.com and kotn.com. Gathering, cleaning, and further analysis was also supported by packages `tidyverse` [@citeTidy], `dplyr` [@citeDplyr], `knitr` [@citeKnit], `kableExtra` [@citeKable], and `RColorBrewer` [@citeRColor].

@@

talk about data collection process and category (women's clothing only)

web scraper chrome extension for kotn (dynamic webpage)

for looping through pagination for zaful

only property we are using is product name

differences/sameness were found by the exact product name so even the difference in colour or size mean they are diff products (this is a lil unfortunate)

summarize total number of products seen before and after for two stores (table woahh)

```{r}
#| label: set-up
#| echo: false
#| message: false
#| warning: false

library(dplyr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(RColorBrewer)

#Read in data
z_products <- read_csv(here::here("inputs/data/zafulapril2.csv"), show_col_types = FALSE)
z_products <- z_products[!duplicated(z_products$products),]

z_products2 <- read_csv(here::here("inputs/data/zafulapril4.csv"), show_col_types = FALSE)
z_products2 <- z_products2[!duplicated(z_products2$products),]

z_products3 <- read_csv(here::here("inputs/data/zafulapril10.csv"), show_col_types = FALSE)
z_products3 <- z_products3[!duplicated(z_products3$products),]

k_products <- read_csv(here::here("inputs/data/kotnapril2.csv"), show_col_types = FALSE)
k_products <- k_products[!duplicated(k_products$products),]

k_products2 <- read_csv(here::here("inputs/data/kotnapril4.csv"), show_col_types = FALSE)
k_products2 <- k_products2[!duplicated(k_products2$products),]

k_products3 <- read_csv(here::here("inputs/data/kotnapril10.csv"), show_col_types = FALSE)
k_products3 <- k_products3[!duplicated(k_products3$products),]

```{r}
#| label: tbl-data
#| tbl-cap: "Total number of Women's Clothing products by store by date"
#| echo: false
#| message: false
#| warning: false

# create data frame of all total products by date by store
totals <- data.frame(
  store = c("ZAFUL (Fast Fashion)", "KOTN (Sustainable)"),
  apr2 = c(nrow(z_products), nrow(k_products)),
  apr4 = c(nrow(z_products2), nrow(k_products2)),
  apr10 = c(nrow(z_products3), nrow(k_products3))
)

# create table displaying data by the dates & store
totals %>% 
  knitr::kable(booktabs = T, linesep = "\\addlinespace", col.names = c("Store", "April 2", "April 4", "April 10")) %>% 
  column_spec(1, bold = T) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  kable_styling(latex_options = "striped")

```{r}
#| label: fig-data
#| fig-cap: "ZAFUL holds much more products overall than KOTN"
#| echo: false
#| message: false
#| warning: false

# create data frame of all information by date and store
totals2 <- data.frame(
  store = c(rep("ZAFUL (Fast Fashion)", times = 3), 
            rep("KOTN (Sustainable)", times = 3)),
  date = c(rep(c("April 2", "April 4", "April 10"), times = 2)),
  products = c(nrow(z_products), nrow(z_products2), nrow(z_products3),
               nrow(k_products), nrow(k_products2), nrow(k_products3))
)

# rename columns and values
date = c("April 2", "April 4", "April 10")
totals2$date <- factor(totals2$date, levels = date)

# create graph of data 
totals2 %>% 
  ggplot(aes(x = date, y = products, fill = store)) +
  geom_col(position = "dodge") + 
  theme_minimal() +
  labs(x = "Date", y = "Products", fill = "Store") + 
  theme(text=element_text(size=11, family="serif")) + 
  scale_fill_brewer(palette = "Set1")

@@

```{r}
#| label: tbl-summary
#| tbl-cap: "Breakdown of added and deprecated products by date shows severity of ZAFUL's rate of production"
#| echo: false
#| message: false
#| warning: false

# Creating subsets of what products are same, added, and removed 
## KOTN Apr 2 -> Apr 4
k_same <- subset(k_products2, (products %in% k_products$products))
k_added <- subset(k_products2, !(products %in% k_products$products))
k_removed <- subset(k_products, !(products %in% k_products2$products))

## KOTN Apr 2 -> Apr 10
k_same2 <- subset(k_products3, (products %in% k_products$products))
k_added2 <- subset(k_products3, !(products %in% k_products$products))
k_added2_1 <- subset(k_products3, !(products %in% k_products2$products))
k_removed2 <- subset(k_products, !(products %in% k_products3$products))
k_removed2_1 <- subset(k_products2, !(products %in% k_products3$products))

## ZAFUL Apr 2 -> Apr 4
z_same <- subset(z_products2, (products %in% z_products$products))
z_added <- subset(z_products2, !(products %in% z_products$products))
z_removed <- subset(z_products, !(products %in% z_products2$products))

## ZAFUL Apr 2 -> Apr 10
z_same2 <- subset(z_products3, (products %in% z_products$products))
z_added2 <- subset(z_products3, !(products %in% z_products$products))
z_added2_1 <- subset(z_products3, !(products %in% z_products2$products))
z_removed2 <- subset(z_products, !(products %in% z_products3$products))
z_removed2_1 <- subset(z_products2, !(products %in% z_products3$products))

#create columns for data frame 
stores <- c("ZAFUL", "", "", "", "", "KOTN", "", "", "", "")
statuses <- c("Total", 
             "Added from April 2", 
             "Deprecated from April 2", 
             "Added from April 4", 
             "Deprecated from April 4", 
             "Total", 
             "Added from April 2", 
             "Deprecated from April 2", 
             "Added from April 4", 
             "Deprecated from April 4")
april2 <- c(nrow(z_products),
           '',
           '',
           '',
           '',
           nrow(k_products),
           '',
           '',
           '',
           '')
april4 <- c(nrow(z_products2),
           nrow(z_added),
           nrow(z_removed),
           '',
           '',
           nrow(k_products2),
           nrow(k_added),
           nrow(k_removed),
           '',
           '')
april10 <- c(nrow(z_products3),
           nrow(z_added2),
           nrow(z_removed2),
           nrow(z_added2_1),
           nrow(z_removed2_1),
           nrow(k_products3),
           nrow(k_added2),
           nrow(k_removed2),
           nrow(k_added2_1),
           nrow(k_removed2_1))

# create data frame of all added and removed data
summary <- data.frame(
  store = stores,
  status = statuses,
  apr2 = april2,
  apr4 = april4,
  apr10 = april10)

# create kable of data frame
summary %>% 
   knitr::kable(booktabs = T, linesep = "\\addlinespace", col.names = c("Store", " ", "April 2", "April 4", "April 10")) %>% 
  column_spec(1:2, bold = T) %>% 
  kable_styling(latex_options = "HOLD_position") %>% 
  kable_styling(latex_options = "striped")
```

```{r}
#| label: tbl-percent
#| tbl-cap: "ZAFUL's percentage of additions and deprecations of products"
#| echo: false
#| message: false
#| warning: false

inc1 <- ((nrow(z_added))/(nrow(z_products)) * 100)
inc2 <- ((nrow(z_added2_1))/(nrow(z_products2)) * 100)
inc3 <- ((nrow(z_added2))/(nrow(z_products)) * 100)

dec1 <- ((nrow(z_removed))/(nrow(z_products)) * 100)
dec2 <- ((nrow(z_removed2_1))/(nrow(z_products2)) * 100)
dec3 <- ((nrow(z_removed2))/(nrow(z_products)) * 100)

percent <- data.frame(
  status = c("Increase (+%)", "Decrease (-%)"),
  apr2to4 = c(inc1, dec1),
  apr2to10 = c(inc2, dec2),
  apr4to10 = c(inc3, dec3)
)

percent %>% 
  knitr::kable(booktabs = T, linesep = "\\addlinespace", col.names = c(" ", "April 2nd to 4th", "April 4th to 10th", "April 2nd to 10th")) %>% 
  column_spec(1, bold = T) %>% 
  kable_styling(latex_options = "HOLD_position")%>% 
  kable_styling(latex_options = "striped")
```

```{r}
#| label: fig-added
#| fig-cap: "Total num of products seem consistent, but the proportion of added ones are large"
#| echo: false
#| message: false
#| warning: false

dates <- c("April 2", "April 4", "April 10")
productss <- c(nrow(z_products), 
               (nrow(z_products2) - nrow(z_added)), 
               (nrow(z_products3) - nrow(z_added2)), as.integer(0), 
               nrow(z_added), 
               nrow(z_added2))

added <- data.frame(
  date = c(rep(dates, times = 2)),
  add = c(rep("Same from Apr 2nd", times = 3), rep("Added", times = 3)),
  products = productss
)

date = c("April 2", "April 4", "April 10")
added$date <- factor(totals2$date, levels = date)

added %>% 
  ggplot(aes(x = date, y = products, fill = add)) +
  geom_col() +
  theme_minimal() +
  labs(x = "Date", y = "Products", fill = "Added?") + 
  theme(text=element_text(size=11, family="serif")) + 
  scale_fill_brewer(palette = "Set1")
```
